%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{letter} % Default font size of the document, change to 10pt to fit more text

\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1.4in % Moves the top of the document 1 inch above the default
\textheight=10in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=7in % Total width of the text, increase this if the left margin was decreased and vice-versa

%\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{Mrs. Jane Smith \\
Recruitment Officer \\
The Corporation \\
123 Pleasant Lane \\
City, State 12345} 

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------
{\large\bf Pavan Kapanipathi} \\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
Kno.e.sis Center \\ Department of Computer Science and Engineering \\ Wright State University  \\ 3640 Colonel Glenn Hwy \\ Dayton, OH, USA 45435-0001 % Your address and phone number

%\signature{Pavan Kapanipathi} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Dear Search Committee,} 

%% Terms to use 
% Big Data
% 

I am currently a Ph.D. student, adviced by Dr. Amit P Sheth in Wright State University. I expect to graduate by Summer 2015. I am writing to apply for the position of Assistant Professor of Computer Science in your department. 

My research interests are in the areas of Semantic Web, Knowledge Graphs, Personalization and Recommendation, Information Retrieval, and Text Mining. My thesis focuses on harnessing knowledge bases for addressing Big Data challenges on social media. My research has provided the basis for invited talks at institutions such as IBM TJ Watson Research Center (Frontiers of Cloud Computing and Big Data Workshop- ), and EMC, CTO Office (Invited Speaker Series- ) at Bangalore. Recently, I presented my research at the Big Data tutorial organized at Wright State University (). I have also contributed to 3 award winning proposals from NSF and NIH at Kno.e.sis. Presently, as a part of one of the NSF funded project, I am working on applying the techniques I developed on use cases in disaster management. 

%% This paragraph is specifically about the collaborations and the university
During the course of my Ph.D., I have collaborated on interesting research problems,  with many local and international researchers from both industry and academia. Few include Google, IBM Research, Samsung Research, DERI (Ireland), and University of Bonn. In future
% IBM and SRA internships 
% IBM Frontiers for Big data and cloud computing and EMC, CTO Office Bangalore

Kno.e.sis provides variety of opportunities and training for an academic career such as: (1) being a part of PC committee member in top conferences such as IJCAI, ESWC, and Hypertext; (2) mentoring students in the lab. This experience has enhanced my passion to pursue an academic career. I am equally committed to and interested in teaching and educational activities. In the attached teaching statement, I have detailed my interests in teaching a variety of undergraduate/graduate courses, and my plans to define new graduate courses when opportunity arises. 

I have asked for three letters of recommendation be sent on my behalf. You would receive the letter from: 

1. Prof. Amit Sheth, LexisNexis Ohio Eminent Scholar, Kno.e.sis, WSU, amit@knoesis.org \\
2. Prof. Krishnaprasad Thirunarayan, Professor, Kno.e.sis, WSU, tkprasad@knoesis.org\\
3. TBA

Additional references can also be obtained from Dr. Prateek Jain, Vice President (Data Science), BlackRock Investments and Dr. Chitra Venkataramani, Program Director, Cognitive Systems Performance Lab, IBM T.J. Watson Research Center. 
\closing{Sincerely yours,}


%\encl{Curriculum vitae, employment form} % List your enclosed documents here, comment this out to get rid of the "encl:"

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}